ABC Group Level Fits

### 2024-01-13 Model/abc_hier.qmd
small chages

Model_Names <- list("EXAM", "Alt_EXAM", "ALM")
Fit_Methods <- list("Test & Train", "Test Only","Train Only")
condits <- list("Constant", "Varied")

# posteriors for each Fit_Method 
teter <- group_posterior_all |> map_dfr(~tibble(pluck(.x$teter_results))) 
te <- group_posterior_all |> map_dfr(~tibble(pluck(.x$te_results))) 
tr <- group_posterior_all |> map_dfr(~tibble(pluck(.x$tr_results)))

@@

ind_abc_s500_ng300_buf5 <- readRDS("~/Library/CloudStorage/GoogleDrive-tegorman13@gmail.com/My Drive/HTW/gl/data/indv_sim/ind_abc_s500_ng300_buf5.rds")

>>>>

@@

# ind_abc_s500_ng300_buf5 <- readRDS("~/Library/CloudStorage/GoogleDrive-tegorman13@gmail.com/My Drive/HTW/gl/data/indv_sim/ind_abc_s500_ng300_buf5.rds")

ind_abc_ss_1000_13_56_52 <- readRDS("~/Library/CloudStorage/GoogleDrive-tegorman13@gmail.com/My Drive/HTW/gl/data/indv_sim/ind_abc_ss_1000_13_56_52.rds")

abc_ev <- ind_abc_ss_1000_13_56_52$id_fits_exam_varied |>
  map_dfr(~tibble(pluck(.x$teter_results)),.id = "id") |> filter(id %in% c(1,2)) |> select(sim_dat) |> unnest(sim_dat) |> filter(rank==1)
